---
title: "Project Proposal"
output: html_notebook
---

## Section 1. Introduction

```{r}
summary(Perfected_Patreon3.0)
```





## Section 2. Data Analysis Plan

1) Fix Data to make it more usable.
2) Find Best Genre, Sub-genre, and Average Income for Patreon Users.
3) Create Graphics.

## Section 3. Data
```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(lubridate)
library(stringr)
```
```{r}
Final_Project_Dataset <- read_csv("../data/patreon2.csv")
```
### Loading .csv File and necessary packages for the assignment

```{r}
music <- "music|house|trap|rap| R&B| classical|funk|pop|hispanic|latin|edm|rock|jazz|ukelele|guitar|piano|drum|covers|music video|Music|House| Trap| Rap| r&b| Classical| Funk| Hispanic|Classical|Funk|Pop|Hispanic|Latin|EDM|Rock|Jazz|Ukelele|Guitar|Piano|Drum|Covers|Music Video| Music Video|MUSIC" 
art <- "art|tutorials|sculpt|paint|render|3D| comic|animation|cartoons|cartoon|NSFW|18+|adult|porn|Porn|Adult|nsfw|18|Cartoon|Cartoons|Animation|CGI|cgi|Render|Tutorials|Art|3D Model|3D model"
podcasts <- "podcast|Podcast|Podcasts|podcasts|Sports|Comedy|Crime|rant|crime|comedy|video game|history|politics"
video <- "video|Video|youtube|ASMR|Vlog|youtube|video essay|gaming|video games|video gaming|reaction|skits|photography|Video|asmr|vlog|YouTube|Video essay|Video Essay|Gaming|Video gaming|Video Gaming|Documentary|documentary|Documentaries|documentaries|Commentary|commentary"
```

### Creating Character Arrays to filter and sift through rows and organize them based on the tags in each array

```{r}
Final_Project_Dataset %>%
  filter(str_detect(Theme, music))
Final_Project_Dataset %>%
  filter(str_detect(Theme, art))
Final_Project_Dataset %>%
  filter(str_detect(Theme, podcasts))
Final_Project_Dataset %>%
  filter(str_detect(Theme, video))
```

### Filtering rows based on Array Categories.

```{r}
Patreon_Video <- Final_Project_Dataset %>%
  filter(str_detect(Theme, video)) %>%
  mutate(Category = "Video")
Patreon_Music <- Final_Project_Dataset %>%
  filter(str_detect(Theme, music)) %>%
  mutate(Category = "Music")
Patreon_Podcast <- Final_Project_Dataset %>%
  filter(str_detect(Theme, podcasts)) %>%
  mutate(Category = "Podcast")
Patreon_Art <- Final_Project_Dataset %>%
  filter(str_detect(Theme, art)) %>%
  mutate(Category = "Art")
```

### Creating new datases to merge into a more usable spreadsheet.

```{r}
Perfected_Patreon <- bind_rows(Patreon_Art,Patreon_Music,Patreon_Podcast,Patreon_Video)
```

### Merging into a more usable spreadsheet.
```{r}
Perfected_Patreon %>%
  group_by(Category) %>%
  ggplot() +
  geom_bar(aes(x = Category)) + labs(Title = "The Most Popular Content Categories", x = "Content Categories", y = "The Number of Content Creators")
```
### Grouping and filtering content to determine which category is the best.
#### Conclusion: Video is the best.

```{r}
Video_Patreon <- Perfected_Patreon %>%
  filter(grepl("Video", Category))
```

### Creating new spreadsheet to find the best subcategory of video content on patreon.

```{r}
YouTube <- "YouTube|youtube|reaction|Reaction"
ASMR <- "ASMR|asmr|a.s.m.r."
gaming <- "Video Games|video games|gaming|game"
documentaries <- "Documentaries|documentaries|documentary"
interviews <- "Interview|interview"
vlog <- "Vlog|vlog"
Commentary <- "Commentary|commentary"
essays <- "Video essay|video essay|Video Essay|history|History"
comedy <- "skit|Skit|Comedy|comedy|humor|Humor"
```

### Repeating Previous steps from line 42-90.

```{r}
Video_Patreon %>%
  filter(str_detect(Theme, YouTube))
Video_Patreon %>%
  filter(str_detect(Theme, ASMR))
Video_Patreon %>%
  filter(str_detect(Theme, gaming))
Video_Patreon %>%
  filter(str_detect(Theme, documentaries))
Video_Patreon %>%
  filter(str_detect(Theme, interviews))
Video_Patreon %>%
  filter(str_detect(Theme, Commentary))
Video_Patreon %>%
  filter(str_detect(Theme, vlog))
Video_Patreon %>%
  filter(str_detect(Theme, essays))
Video_Patreon %>%
  filter(str_detect(Theme, comedy))
```


```{r}
Patreon_YouTube <- Video_Patreon %>%
  filter(str_detect(Theme, YouTube)) %>%
  mutate(Subcategory = "YouTuber")
Patreon_ASMR <- Video_Patreon %>%
  filter(str_detect(Theme, ASMR)) %>%
  mutate(Subcategory = "ASMR")
Patreon_Gaming <- Video_Patreon %>%
  filter(str_detect(Theme, gaming)) %>%
  mutate(Subcategory = "Video Games")
Patreon_Documentary <- Video_Patreon %>%
  filter(str_detect(Theme, documentaries)) %>%
  mutate(Subcategory = "Docuseries")
Patreon_Interview <- Video_Patreon %>%
  filter(str_detect(Theme, interviews)) %>%
  mutate(Subcategory = "Interviewing")
Patreon_Commentator <- Video_Patreon %>%
  filter(str_detect(Theme, Commentary)) %>%
  mutate(Subcategory = "Commentator")
Patreon_Vlog <- Video_Patreon %>%
  filter(str_detect(Theme, vlog)) %>%
  mutate(Subcategory = "Vlogger")
Patreon_Essay <- Video_Patreon %>%
  filter(str_detect(Theme, essays)) %>%
  mutate(Subcategory = "Video Essay")
Patreon_Comedy <- Video_Patreon %>%
  filter(str_detect(Theme, comedy)) %>%
  mutate(subcategory = "Comedian")
```


```{r}
Patreon_Video_2.0 <- bind_rows(Patreon_ASMR,Patreon_Comedy,Patreon_Commentator,Patreon_Documentary,Patreon_Essay,Patreon_Gaming,Patreon_Interview,Patreon_YouTube)
```


```{r}
Patreon_Video_2.0 %>%
  group_by(Subcategory) %>%
  ggplot() +
  geom_bar(aes(x = Subcategory)) + labs(x = "Types of Videos", y = "The Number of Content Creators")
```


```{r}
Perfected_Patreon3.0 <- Perfected_Patreon %>%
  mutate(Per_Patron2.0 = str_extract(`Per patron`,"\\d+\\.*\\d+"),
         Per_Patron2.0 = as.numeric(Per_Patron2.0)) %>%
  mutate(Income_By_Thousand = str_extract(`Earnings`,"\\d+"),
         Income_By_Thousand = as.numeric(Income_By_Thousand))
  
```

## Extracting digits in character strings into more usbale numerical values 

```{r}
Perfected_Patreon3.0 %>%
  ggplot() + geom_pointt(aes(y = `Income_By_Thousand`, x = `Patrons`, na.rm = TRUE))
```
## Graphical experiments

```{r}
Perfected_Patreon3.0 %>%
  ggplot() + geom_boxplot(aes(x = `Income_By_Thousand`, na.rm = TRUE))
```



```{r}
Perfected_Patreon3.0 %>%
  summarise(Average_Price = mean(`Per_Patron2.0`, na.rm = TRUE))
Perfected_Patreon3.0 %>%
  summarise(Average_Time = mean(`Days Running`/365, na.rm = TRUE))
Perfected_Patreon3.0 %>%
  summarise(Average_Earnings = mean(`Income_By_Thousand`, na.rm = TRUE))
```

## Answering simple question regarding averages for numerical values.